Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-11 scagnostics.Rmd
as.tibble warning fixed

```{r datasetFunctions}
sphereData <- function(n, p){
  dRet <- geozoo::sphere.solid.random(n,p)
  return(as.tibble(dRet$points))
}

pipeData <- function(n, p){
  i <- 1
  dRet <- NULL
  while(i <= p){
    v <- runif(n, -1, 1)
    if(abs(v[n-1]*v[n-1] + v[n]*v[n] - 1) < 0.1){
      dRet <- rbind(dRet, v)
      i <- i+1
    }
  }
  return(as.tibble(dRet))
}

sinData <- function(n, p){
  vName <- paste0("V",n)
  vNameM1 <- paste0("V",n-1)
  expr <- paste0(vName,"=sin(",vNameM1,")") # need string expression if I want to use tibble here
  dRet <- as.tibble(matrix(rnorm((n-1)*p), ncol=(n-1))) #generate normal distributed n-1 dim data
  dRet <- mutate_(dRet, expr) #string evaluation calculates var(n) as tan(var(n-1))
  colnames(dRet)[n] <- vName #correct name of new variable
  dRet[vName] <- jitter(dRet[[vName]]) #adding noise
  return(dRet)
}

@@

```{r findsine, fig.width=6, fig.height=7, out.width = "0.8\\textwidth", fig.cap="Guided tour optimising  the splines2d index, using method 3, for the sine data, with $n=1000$. Anchor planes are marked by the blue vertical lines, and are closer to each other approaching the maxima. The sine is found relatively easily, by splines2D, and it is indicated that MIC, TIC, dcor2D and convex would also likely find this structure.", results="hide"}
set.seed(2018)
if(!file.exists("cache/findsine.rda")){
  sineResc <- as.matrix(sin1000)
  sineTour <- save_history(sineResc,
                          guided_tour(splineIndex()))
  sineTourFull <- as.list(interpolate(sineTour))
  sineTourRes <- getProj(sin1000, sineTourFull, "Sine", 1000)
  #sineTourResMelt <- melt(sineTourRes, id=c("t", "name", "size"))
  #save(sineResc, sineTour, sineTourFull, sineTourRes, sineTourResMelt, file = "cache/findsine.rda")
  save(sineResc, sineTour, sineTourFull, sineTourRes, file = "cache/findsine.rda")
} else {
  load("cache/findsine.rda")
}
anchorIdx <- as.tibble(which(attributes(interpolate(sineTour))$new_basis))
sineTourResMelt <-sineTourRes %>%
  mutate(convex = 1-convex) %>%
  rowwise() %>%
  mutate(holes = rescaleHoles(holes)) %>%
  select(-cmass) %>%
  gather(variable, value, -t, -name, -size) %>%
  mutate(variable = fct_relevel(variable, "holes", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
ggplot(sineTourResMelt, aes(x=t, y=value)) +
  geom_line(mapping=aes(color=(variable=="splines2d"))) + 
  facet_wrap(~variable, ncol=1, scales = "free_y") +
  scale_colour_manual(values = c("black", "red")) +
  facet_wrap(~variable, ncol=1, strip.position = "right") +
  geom_vline(data=anchorIdx, mapping=aes(xintercept=value), color="blue", alpha=0.3) +
  guides(color=FALSE) +
  ylim(c(0,1)) + xlab("Number of projections") + ylab("PPI value")
```

@@

  maxBases <- 100
#  maxBases <- 1000
  fViewL <- list()
  allPlanes <- list()
  i <- 1
  for(d in c(4,5,6)){
  #d = 6
    set.seed(58958)
    specialPlane <- matrix(c(rep(0,d-2),1,0,rep(0,d-1),1),ncol=2)
    spiralD <- spiral1000 %>%
      purrr::when(d<6 ~ select(., -V4), ~ .) %>%
      purrr::when(d<5 ~ select(., -V3), ~ .)
    spiralTour <- save_history(as.matrix(spiralD),
                               guided_tour(scagIndex("Skinny"), 
                                  search_f = tourr:::search_better,
                                  max.tries = 5000, 
                                  #max.tries = 50000, 
                                  cooling = 1, alpha = pi),
                              max_bases = maxBases)
    #if(d==4){maxBases <- min(maxBases, length(spiralTour))}
    nBases <- length(spiralTour)
    distDf <- rbind(distDf, tibble(d=d, distance=distanceDist(spiralTour)))
    distToSp <- rbind(distToSp, tibble(d=d, distance=distanceToSp(spiralTour, specialPlane), t=1:nBases))
    fView <- as.tibble(as.matrix(spiralD) %*% as.list(spiralTour)[[nBases]])
    fViewL[[i]] <- ggplot(fView, aes(V1, V2)) + geom_point()
    allPlanes[[i]] <- spiralTour
    i <- i+1
  }
  save(distDf, distToSp, fViewL, allPlanes, file = "cache/findspiral.rda")
} else {
  load("cache/findspiral.rda")
}

@@

```{r neutronStarEq,  results="hide"}
nsD <- read_csv("data/samples.csv") 
nsM <- nsD %>%
  select(-m2) %>% # remove m2 to avoid finding well known correlation
  rescale() # rescaling, this returns a matrix
if(!file.exists("cache/neutronStarEq.rda")){
  set.seed(2018)
  nseTour <- save_history(nsM, guided_tour(splineIndex()))
  nseTourFull <- as.list(interpolate(nseTour))
  save(nseTour, nseTourFull, file = "cache/neutronStarEq.rda")
} else {
  load("cache/neutronStarEq.rda")
}
iLast <- length(nseTourFull)
fProj <- nseTourFull[[iLast]]
dProj <- as.tibble(nsM %*% fProj)
colnames(fProj) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj <- as_tibble(fProj) %>%
  add_column(label=colnames(nsM))
```

@@

```{r nseRemL1, fig.cap="Removing L1 and optimise again of the remaining parameters, where m2 remains removed from the set. Because of parameter correlations we can recover clear description of L2 as a function of the other parameters, despite m2 missing."}
nsM2 <- nsD %>%
  select(-m2, -L1) %>% # remove m2 to avoid finding well known correlation
  rescale()
if(!file.exists("cache/neutronRemL1.rda")){
  set.seed(2018)
  nseTour2 <- save_history(nsM2, guided_tour(splineIndex()))
  save(nseTour2, file = "cache/neutronRemL1.rda")
} else{
  load("cache/neutronRemL1.rda")
}
tL <- as.list(nseTour2)
iLast <- length(tL)
fProj <- tL[[iLast]]
dProj <- as.tibble(nsM2 %*% fProj)
colnames(fProj) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj <- as_tibble(fProj) %>%
  add_column(label=colnames(nsM2))
p1 <- ggplot(as.tibble(dProj), aes(PP1, PP2))+geom_point(alpha=0.1)+ theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.5,0.6,0.3,0.18), aes(x=x, y=y), color="grey") + 
  xlim(0, 1.5) + ylim(-0.1, 0.8) +
  geom_segment(data=getAxes(fProj, 0.5,0.6,0.3,0.18), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj, 0.5,0.6,0.3,0.18), aes(x=x2, y=y2, label=label), size=2.5)
p2 <- ggplot(as.tibble(nsM2), aes(m1+R1+1.5*R2, L2)) + geom_point(alpha=0.1)+ theme(aspect.ratio=1)
p3 <- ggplot(nsD, aes(R2/m2, L2))+ geom_point(alpha=0.1)+ theme(aspect.ratio=1)
grid.arrange(p1, p2, p3, ncol=3)
```

@@

iLast <- length(bbhTourFull1)
fProj1 <- bbhTourFull1[[iLast]]
dProj1 <- as.tibble(bbhM %*% fProj1)
colnames(fProj1) <- c("PP1", "PP2")
colnames(dProj1) <- c("PP1", "PP2")
fProj1 <- as_tibble(fProj1) %>%
  add_column(label=colnames(bbhM))
p1 <- ggplot(dProj1, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.4,0.5,0.26,0.24), aes(x=x, y=y), color="grey") + 
  xlim(0.1, 1.4) + ylim(-0.3, 0.9) +
  geom_segment(data=getAxes(fProj1, 0.4,0.5,0.26,0.24), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj1, 0.4,0.5,0.26,0.24), aes(x=x2, y=y2, label=label), size=2.5) + ggtitle("a. TIC: 779.46")
iLast <- length(bbhTourFull2)
fProj2 <- bbhTourFull2[[iLast]]
dProj2 <- as.tibble(bbhM %*% fProj2)
colnames(fProj2) <- c("PP1", "PP2")
colnames(dProj2) <- c("PP1", "PP2")
fProj2 <- as_tibble(fProj2) %>%
  add_column(label=colnames(bbhM))
p2 <- ggplot(dProj2, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.3,-1,0.24,0.22), aes(x=x, y=y), color="grey") + 
  xlim(-0.1, 1.1) + ylim(-1.3, -0.2) +
  geom_segment(data=getAxes(fProj2,0.3,-1,0.24,0.22), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj2, 0.3,-1,0.24,0.22), aes(x=x2, y=y2, label=label), size=2.5) + ggtitle("b. splines2D: 0.97")
iLast <- length(bbhTourFull3)
fProj3 <- bbhTourFull3[[iLast]]
dProj3 <- as.tibble(bbhM %*% fProj3)
colnames(fProj3) <- c("PP1", "PP2")
colnames(dProj3) <- c("PP1", "PP2")
fProj3 <- as_tibble(fProj3) %>%
  add_column(label=colnames(bbhM))
p3 <- ggplot(dProj3, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.75, 1, 0.3, 0.28), aes(x=x, y=y), color="grey") + 
  xlim(-0.2, 1.3) + ylim(-0.1, 1.3) +
  geom_segment(data=getAxes(fProj3,0.75, 1, 0.3, 0.28), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj3, 0.75, 1, 0.3, 0.28), aes(x=x2, y=y2, label=label), size=2.5) + ggtitle("c. 1-convex: 0.50")
grid.arrange(p1, p2, p3, ncol=3) 
```

@@

iLast <- length(bbhTourFull12)
fProj1 <- bbhTourFull12[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj1)
colnames(fProj1) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj1 <- as_tibble(fProj1) %>%
  add_column(label=colnames(bbhM2))
iv <- mine(dProj$PP1,dProj$PP2)["TIC"]
p1 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(1, 0, 0.34, 0.25), aes(x=x, y=y), color="grey") + 
  xlim(-0.2, 1.5) + ylim(-0.25, 1) +
  geom_segment(data=getAxes(fProj1,1, 0, 0.34, 0.25), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj1, 1, 0, 0.34, 0.25), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("a, TIC: ", toString(format(iv, digits=2))))
iLast <- length(bbhTourFull22)
fProj2 <- bbhTourFull22[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj2)
colnames(fProj2) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj2 <- as_tibble(fProj2) %>%
  add_column(label=colnames(bbhM2))
iv <- splines2d(dProj$PP1,dProj$PP2)
p2 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0.75, 0, 0.25, 0.24), aes(x=x, y=y), color="grey") + 
  xlim(-0.25, 1) + ylim(-0.9, 0.3) +
  geom_segment(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("b, splines2D: ", toString(format(iv, digits=2))))
iLast <- length(bbhTourFull32)
fProj3 <- bbhTourFull32[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj3)
colnames(fProj3) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj3 <- as_tibble(fProj3) %>%
  add_column(label=colnames(bbhM2))
iv <- 1-scagnostics(as.matrix(dProj))[,"Convex"]
p3 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0, 1.25, 0.32, 0.32), aes(x=x, y=y), color="grey") + 
  xlim(-0.4, 1.2) + ylim(0, 1.6) +
  geom_segment(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("c, 1-convex: ", toString(format(iv, digits=2))))
grid.arrange(p1, p2, p3, ncol=3) 
```

@@

if(!file.exists("cache/bbhGuidedSpline3.rda")){
  set.seed(2018)
  seedVals <- sample(1:10000, 6)
  bbhRes1 <- getResWithSeed(seedVals[1])
  bbhRes2 <- getResWithSeed(seedVals[2])
  bbhRes3 <- getResWithSeed(seedVals[3])
  bbhRes4 <- getResWithSeed(seedVals[4])
  bbhRes5 <- getResWithSeed(seedVals[5])
  bbhRes6 <- getResWithSeed(seedVals[6])
  save(bbhRes1, bbhRes2, bbhRes3, bbhRes4, bbhRes5, bbhRes6, file = "cache/bbhGuidedSpline3.rda")
} else {
  load("cache/bbhGuidedSpline3.rda")
}
resList <- list(as.list(bbhRes1), as.list(bbhRes2), as.list(bbhRes3),
                as.list(bbhRes4), as.list(bbhRes5), as.list(bbhRes6))
pList <- list()
idxV <- NULL
i <- 1
xmins <- c(-0.5,-0.5,-0.4,-0.9,-1,0.25)
xmaxs <- c(0.75,0.75,0.8,0.4,0.25,1.5)
ymins <- c(-0.8,-0.8,-0.7,-0.8,-1.2,-0.6)
ymaxs <- c(0.7,0.6,0.7,0.7,0.,0.9)
xscales <- c(0.25,0.25,0.24,0.26,0.25,0.25)
yscales <- c(0.3,0.28,0.28,0.3,0.24,0.3)
xcents <- c(0.25,-0.25,-0.1,0.1,-0.75,1.25)
ycents <- c(0.4,-0.4,-0.4,-0.4,-0.75,0.5)
titleL <- c("a: ","b: ","c: ","d: ","f: ","e: ")
for (r in resList){
  iLast <- length(r)
  fProj <- r[[iLast]]
  dProj <- as.tibble(bbhM3 %*% fProj)
  colnames(fProj) <- c("PP1", "PP2")
  colnames(dProj) <- c("PP1", "PP2")
  fProj <- as_tibble(fProj) %>%
    add_column(label=colnames(bbhM3))
  idxV <- splines2d(dProj$PP1, dProj$PP2)
  pList[[i]] <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(xcents[i],ycents[i],xscales[i],yscales[i]), aes(x=x, y=y), color="grey") + 
  xlim(xmins[i], xmaxs[i]) + ylim(ymins[i], ymaxs[i]) +
  geom_segment(data=getAxes(fProj, xcents[i],ycents[i],xscales[i],yscales[i]), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj, xcents[i],ycents[i],xscales[i],yscales[i]), aes(x=x2, y=y2, label=label), size=2.5) +
    ggtitle(paste0(titleL[i], toString(format(idxV, digits=2))))
  i <- i+1
}
grid.arrange(pList[[1]], pList[[2]], pList[[3]],pList[[4]], pList[[6]], pList[[5]], ncol=3)
```

>>>>

```{r datasetFunctions}
sphereData <- function(n, p){
  dRet <- geozoo::sphere.solid.random(n,p)
  return(as_tibble(dRet$points))
}

pipeData <- function(n, p){
  i <- 1
  dRet <- NULL
  while(i <= p){
    v <- runif(n, -1, 1)
    if(abs(v[n-1]*v[n-1] + v[n]*v[n] - 1) < 0.1){
      dRet <- rbind(dRet, v)
      i <- i+1
    }
  }
  return(as_tibble(dRet))
}

sinData <- function(n, p){
  vName <- paste0("V",n)
  vNameM1 <- paste0("V",n-1)
  expr <- paste0(vName,"=sin(",vNameM1,")") # need string expression if I want to use tibble here
  dRet <- as_tibble(matrix(rnorm((n-1)*p), ncol=(n-1))) #generate normal distributed n-1 dim data
  dRet <- mutate_(dRet, expr) #string evaluation calculates var(n) as tan(var(n-1))
  colnames(dRet)[n] <- vName #correct name of new variable
  dRet[vName] <- jitter(dRet[[vName]]) #adding noise
  return(dRet)
}

@@

```{r findsine, fig.width=6, fig.height=7, out.width = "0.8\\textwidth", fig.cap="Guided tour optimising  the splines2d index, using method 3, for the sine data, with $n=1000$. Anchor planes are marked by the blue vertical lines, and are closer to each other approaching the maxima. The sine is found relatively easily, by splines2D, and it is indicated that MIC, TIC, dcor2D and convex would also likely find this structure.", results="hide"}
set.seed(2018)
if(!file.exists("cache/findsine.rda")){
  sineResc <- as.matrix(sin1000)
  sineTour <- save_history(sineResc,
                          guided_tour(splineIndex()))
  sineTourFull <- as.list(interpolate(sineTour))
  sineTourRes <- getProj(sin1000, sineTourFull, "Sine", 1000)
  #sineTourResMelt <- melt(sineTourRes, id=c("t", "name", "size"))
  #save(sineResc, sineTour, sineTourFull, sineTourRes, sineTourResMelt, file = "cache/findsine.rda")
  save(sineResc, sineTour, sineTourFull, sineTourRes, file = "cache/findsine.rda")
} else {
  load("cache/findsine.rda")
}
anchorIdx <- as_tibble(which(attributes(interpolate(sineTour))$new_basis))
sineTourResMelt <-sineTourRes %>%
  mutate(convex = 1-convex) %>%
  rowwise() %>%
  mutate(holes = rescaleHoles(holes)) %>%
  select(-cmass) %>%
  gather(variable, value, -t, -name, -size) %>%
  mutate(variable = fct_relevel(variable, "holes", "convex", "skinny", "stringy", "dcor2d", "splines2d", "MIC", "TIC"))
ggplot(sineTourResMelt, aes(x=t, y=value)) +
  geom_line(mapping=aes(color=(variable=="splines2d"))) + 
  facet_wrap(~variable, ncol=1, scales = "free_y") +
  scale_colour_manual(values = c("black", "red")) +
  facet_wrap(~variable, ncol=1, strip.position = "right") +
  geom_vline(data=anchorIdx, mapping=aes(xintercept=value), color="blue", alpha=0.3) +
  guides(color=FALSE) +
  ylim(c(0,1)) + xlab("Number of projections") + ylab("PPI value")
```

@@

  maxBases <- 100
#  maxBases <- 1000
  fViewL <- list()
  allPlanes <- list()
  i <- 1
  for(d in c(4,5,6)){
  #d = 6
    set.seed(58958)
    specialPlane <- matrix(c(rep(0,d-2),1,0,rep(0,d-1),1),ncol=2)
    spiralD <- spiral1000 %>%
      purrr::when(d<6 ~ select(., -V4), ~ .) %>%
      purrr::when(d<5 ~ select(., -V3), ~ .)
    spiralTour <- save_history(as.matrix(spiralD),
                               guided_tour(scagIndex("Skinny"), 
                                  search_f = tourr:::search_better,
                                  max.tries = 5000, 
                                  #max.tries = 50000, 
                                  cooling = 1, alpha = pi),
                              max_bases = maxBases)
    #if(d==4){maxBases <- min(maxBases, length(spiralTour))}
    nBases <- length(spiralTour)
    distDf <- rbind(distDf, tibble(d=d, distance=distanceDist(spiralTour)))
    distToSp <- rbind(distToSp, tibble(d=d, distance=distanceToSp(spiralTour, specialPlane), t=1:nBases))
    fView <- as_tibble(as.matrix(spiralD) %*% as.list(spiralTour)[[nBases]])
    fViewL[[i]] <- ggplot(fView, aes(V1, V2)) + geom_point()
    allPlanes[[i]] <- spiralTour
    i <- i+1
  }
  save(distDf, distToSp, fViewL, allPlanes, file = "cache/findspiral.rda")
} else {
  load("cache/findspiral.rda")
}

@@

```{r neutronStarEq,  results="hide"}
nsD <- read_csv("data/samples.csv") 
nsM <- nsD %>%
  select(-m2) %>% # remove m2 to avoid finding well known correlation
  rescale() # rescaling, this returns a matrix
if(!file.exists("cache/neutronStarEq.rda")){
  set.seed(2018)
  nseTour <- save_history(nsM, guided_tour(splineIndex()))
  nseTourFull <- as.list(interpolate(nseTour))
  save(nseTour, nseTourFull, file = "cache/neutronStarEq.rda")
} else {
  load("cache/neutronStarEq.rda")
}
iLast <- length(nseTourFull)
fProj <- nseTourFull[[iLast]]
dProj <- as_tibble(nsM %*% fProj)
colnames(fProj) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj <- as_tibble(fProj) %>%
  add_column(label=colnames(nsM))
```

@@

```{r nseRemL1, fig.cap="Removing L1 and optimise again of the remaining parameters, where m2 remains removed from the set. Because of parameter correlations we can recover clear description of L2 as a function of the other parameters, despite m2 missing."}
nsM2 <- nsD %>%
  select(-m2, -L1) %>% # remove m2 to avoid finding well known correlation
  rescale()
if(!file.exists("cache/neutronRemL1.rda")){
  set.seed(2018)
  nseTour2 <- save_history(nsM2, guided_tour(splineIndex()))
  save(nseTour2, file = "cache/neutronRemL1.rda")
} else{
  load("cache/neutronRemL1.rda")
}
tL <- as.list(nseTour2)
iLast <- length(tL)
fProj <- tL[[iLast]]
dProj <- as_tibble(nsM2 %*% fProj)
colnames(fProj) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj <- as_tibble(fProj) %>%
  add_column(label=colnames(nsM2))
p1 <- ggplot(as_tibble(dProj), aes(PP1, PP2))+geom_point(alpha=0.1)+ theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.5,0.6,0.3,0.18), aes(x=x, y=y), color="grey") + 
  xlim(0, 1.5) + ylim(-0.1, 0.8) +
  geom_segment(data=getAxes(fProj, 0.5,0.6,0.3,0.18), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj, 0.5,0.6,0.3,0.18), aes(x=x2, y=y2, label=label), size=2.5)
p2 <- ggplot(as_tibble(nsM2), aes(m1+R1+1.5*R2, L2)) + geom_point(alpha=0.1)+ theme(aspect.ratio=1)
p3 <- ggplot(nsD, aes(R2/m2, L2))+ geom_point(alpha=0.1)+ theme(aspect.ratio=1)
grid.arrange(p1, p2, p3, ncol=3)
```

@@

iLast <- length(bbhTourFull1)
fProj1 <- bbhTourFull1[[iLast]]
dProj1 <- as_tibble(bbhM %*% fProj1)
colnames(fProj1) <- c("PP1", "PP2")
colnames(dProj1) <- c("PP1", "PP2")
fProj1 <- as_tibble(fProj1) %>%
  add_column(label=colnames(bbhM))
p1 <- ggplot(dProj1, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.4,0.5,0.26,0.24), aes(x=x, y=y), color="grey") + 
  xlim(0.1, 1.4) + ylim(-0.3, 0.9) +
  geom_segment(data=getAxes(fProj1, 0.4,0.5,0.26,0.24), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj1, 0.4,0.5,0.26,0.24), aes(x=x2, y=y2, label=label), size=2.5) + ggtitle("a. TIC: 779.46")
iLast <- length(bbhTourFull2)
fProj2 <- bbhTourFull2[[iLast]]
dProj2 <- as_tibble(bbhM %*% fProj2)
colnames(fProj2) <- c("PP1", "PP2")
colnames(dProj2) <- c("PP1", "PP2")
fProj2 <- as_tibble(fProj2) %>%
  add_column(label=colnames(bbhM))
p2 <- ggplot(dProj2, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.3,-1,0.24,0.22), aes(x=x, y=y), color="grey") + 
  xlim(-0.1, 1.1) + ylim(-1.3, -0.2) +
  geom_segment(data=getAxes(fProj2,0.3,-1,0.24,0.22), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj2, 0.3,-1,0.24,0.22), aes(x=x2, y=y2, label=label), size=2.5) + ggtitle("b. splines2D: 0.97")
iLast <- length(bbhTourFull3)
fProj3 <- bbhTourFull3[[iLast]]
dProj3 <- as_tibble(bbhM %*% fProj3)
colnames(fProj3) <- c("PP1", "PP2")
colnames(dProj3) <- c("PP1", "PP2")
fProj3 <- as_tibble(fProj3) %>%
  add_column(label=colnames(bbhM))
p3 <- ggplot(dProj3, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(0.75, 1, 0.3, 0.28), aes(x=x, y=y), color="grey") + 
  xlim(-0.2, 1.3) + ylim(-0.1, 1.3) +
  geom_segment(data=getAxes(fProj3,0.75, 1, 0.3, 0.28), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj3, 0.75, 1, 0.3, 0.28), aes(x=x2, y=y2, label=label), size=2.5) + ggtitle("c. 1-convex: 0.50")
grid.arrange(p1, p2, p3, ncol=3) 
```

@@

iLast <- length(bbhTourFull12)
fProj1 <- bbhTourFull12[[iLast]]
dProj <- as_tibble(bbhM2 %*% fProj1)
colnames(fProj1) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj1 <- as_tibble(fProj1) %>%
  add_column(label=colnames(bbhM2))
iv <- mine(dProj$PP1,dProj$PP2)["TIC"]
p1 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(1, 0, 0.34, 0.25), aes(x=x, y=y), color="grey") + 
  xlim(-0.2, 1.5) + ylim(-0.25, 1) +
  geom_segment(data=getAxes(fProj1,1, 0, 0.34, 0.25), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj1, 1, 0, 0.34, 0.25), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("a, TIC: ", toString(format(iv, digits=2))))
iLast <- length(bbhTourFull22)
fProj2 <- bbhTourFull22[[iLast]]
dProj <- as_tibble(bbhM2 %*% fProj2)
colnames(fProj2) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj2 <- as_tibble(fProj2) %>%
  add_column(label=colnames(bbhM2))
iv <- splines2d(dProj$PP1,dProj$PP2)
p2 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0.75, 0, 0.25, 0.24), aes(x=x, y=y), color="grey") + 
  xlim(-0.25, 1) + ylim(-0.9, 0.3) +
  geom_segment(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("b, splines2D: ", toString(format(iv, digits=2))))
iLast <- length(bbhTourFull32)
fProj3 <- bbhTourFull32[[iLast]]
dProj <- as_tibble(bbhM2 %*% fProj3)
colnames(fProj3) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj3 <- as_tibble(fProj3) %>%
  add_column(label=colnames(bbhM2))
iv <- 1-scagnostics(as.matrix(dProj))[,"Convex"]
p3 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0, 1.25, 0.32, 0.32), aes(x=x, y=y), color="grey") + 
  xlim(-0.4, 1.2) + ylim(0, 1.6) +
  geom_segment(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("c, 1-convex: ", toString(format(iv, digits=2))))
grid.arrange(p1, p2, p3, ncol=3) 
```

@@

if(!file.exists("cache/bbhGuidedSpline3.rda")){
  set.seed(2018)
  seedVals <- sample(1:10000, 6)
  bbhRes1 <- getResWithSeed(seedVals[1])
  bbhRes2 <- getResWithSeed(seedVals[2])
  bbhRes3 <- getResWithSeed(seedVals[3])
  bbhRes4 <- getResWithSeed(seedVals[4])
  bbhRes5 <- getResWithSeed(seedVals[5])
  bbhRes6 <- getResWithSeed(seedVals[6])
  save(bbhRes1, bbhRes2, bbhRes3, bbhRes4, bbhRes5, bbhRes6, file = "cache/bbhGuidedSpline3.rda")
} else {
  load("cache/bbhGuidedSpline3.rda")
}
resList <- list(as.list(bbhRes1), as.list(bbhRes2), as.list(bbhRes3),
                as.list(bbhRes4), as.list(bbhRes5), as.list(bbhRes6))
pList <- list()
idxV <- NULL
i <- 1
xmins <- c(-0.5,-0.5,-0.4,-0.9,-1,0.25)
xmaxs <- c(0.75,0.75,0.8,0.4,0.25,1.5)
ymins <- c(-0.8,-0.8,-0.7,-0.8,-1.2,-0.6)
ymaxs <- c(0.7,0.6,0.7,0.7,0.,0.9)
xscales <- c(0.25,0.25,0.24,0.26,0.25,0.25)
yscales <- c(0.3,0.28,0.28,0.3,0.24,0.3)
xcents <- c(0.25,-0.25,-0.1,0.1,-0.75,1.25)
ycents <- c(0.4,-0.4,-0.4,-0.4,-0.75,0.5)
titleL <- c("a: ","b: ","c: ","d: ","f: ","e: ")
for (r in resList){
  iLast <- length(r)
  fProj <- r[[iLast]]
  dProj <- as_tibble(bbhM3 %*% fProj)
  colnames(fProj) <- c("PP1", "PP2")
  colnames(dProj) <- c("PP1", "PP2")
  fProj <- as_tibble(fProj) %>%
    add_column(label=colnames(bbhM3))
  idxV <- splines2d(dProj$PP1, dProj$PP2)
  pList[[i]] <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(xcents[i],ycents[i],xscales[i],yscales[i]), aes(x=x, y=y), color="grey") + 
  xlim(xmins[i], xmaxs[i]) + ylim(ymins[i], ymaxs[i]) +
  geom_segment(data=getAxes(fProj, xcents[i],ycents[i],xscales[i],yscales[i]), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj, xcents[i],ycents[i],xscales[i],yscales[i]), aes(x=x2, y=y2, label=label), size=2.5) +
    ggtitle(paste0(titleL[i], toString(format(idxV, digits=2))))
  i <- i+1
}
grid.arrange(pList[[1]], pList[[2]], pList[[3]],pList[[4]], pList[[6]], pList[[5]], ncol=3)
```
